Performance Models for Data Transfers: A Case Study with Molecular Chemistry Kernels

### 2019-04-11 ICPP-19/communications.tex
redrawing plots

	Given a schedule, \scomm($i$) and \scomp($i$) represent the
	start times of task $i$ on communication and computation
	resources. A schedule is feasible if for every time $t$, the
	amount of memory required by all tasks such that $\scomm(i) \leq t
	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
	$C$. 
	\todo[inline]{SKumar: We do not need this assumption everywhere. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof.}
	For simplicity, we assume in all of this paper that the
	amount of memory required by a task is proportional to its
	communication time, and without loss of generality we consider
	that memory size of a task is equal to its communication time.

@@

		\todo[inline]{SKumar: will do}
		\begin{figure}[htb]
			%\begin{tabular}{c}
			\includegraphics[scale=0.5]{./results/plots/application_properties.pdf}
			\caption{HF and CCSD tasks characteristics.\todo[inline]{ylab(``Ratio to optimal'') (or to OSIM). Ideally remove underscores from the X axis.}}
			\label{fig:ApplicationProperties}
		\end{figure}

@@

		Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} show the distribution of the performance of each heuristic for all considered memory capacities, where plots are categorized by memory capacities. For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
		\subsection{HF Performance}	
		%%	\begin{figure*}[htb]
		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_hf.pdf}
		%%		\caption{Comparison of different heuristics for HF.}
		%%		\label{fig:ratio_to_optimal_hf}
		%%	\end{figure*}
		\begin{figure*}[htb]
			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
			\caption{Comparison of different heuristics for HF.\todo[inline]{LED: Wouldn't it be easier to read if facet labels were expressed as ratios of $m_c$ ($1$, $1.125$, $1.25$, ...) instead of absolute values?. Here also, ylab(``Ratio to optimal'')}}
			\label{fig:ratio_to_optimal_hf}
		\end{figure*}

@@

		\begin{figure}[htb]
			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
			\caption{Comparision of best variants of all categories for HF.\todo[inline]{LED: I still believe you should plot the actual ratio $r$ and not $1/r$. Since I am not sure how to redo the plots I will let you do it. Also ylab(``Ratio to optimal'') please (or more explicitley, to OSIM?). And make sure to write ``Best static'' and remove underscores. You can use plyr::revalue for that.} }
			\label{fig:ratio_to_optimal_best_hf}
		\end{figure}

@@

		\begin{figure}[htb]
			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
			\caption{Comparision of best variants of all categories for CCSD.}
			\label{fig:ratio_to_optimal_best_ccsd}
		\end{figure}

@@

		\begin{figure*}[htb]
			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_batch-best.pdf}
			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.\todo[inline]{LED: Here also I believe you should plot the actual ratio $r$ and not $1/r$.}}
			\label{fig:best_variants_batch}
		\end{figure*}

>>>>

	Given a schedule, \scomm($i$) and \scomp($i$) represent the
	start times of task $i$ on communication and computation
	resources. A schedule is feasible if for every time $t$, the
	amount of memory required by all tasks such that $\scomm(i) \leq t
	\leq \scomp(i) + COMP_i$ is not more than the memory capacity
	$C$. 
	\todo[inline]{SKumar: We do not need this assumption throughout the paper. CommVolume=CommTime is not true for experimental section. We used this assumption only in NP-hard proof for simplicity.}
	For simplicity, we assume in all of this paper that the
	amount of memory required by a task is proportional to its
	communication time, and without loss of generality we consider
	that memory size of a task is equal to its communication time.

@@

		\begin{figure}[htb]
			%\begin{tabular}{c}
			\includegraphics[scale=0.5]{./results/plots/application_properties.pdf}
			\caption{HF and CCSD tasks characteristics.}
%%				\todo[inline]{ylab(``Ratio to optimal'') (or to OSIM). Ideally remove underscores from the X axis.}
			\label{fig:ApplicationProperties}
		\end{figure}

@@

		Figures ~\ref{fig:ratio_to_optimal_hf} and ~\ref{fig:ratio_to_optimal_ccsd} show the distribution of the performance of each heuristic for all considered memory capacities, where plots are categorized by memory capacities. For each memory capacity and each heuristic, the box on the plot displays the median, first and last quartile, and the whiskers indicate minimum and maximum values, with outliers are shown by black dots.
		\subsection{HF Performance}	
		%%	\begin{figure*}[htb]
		%%		\includegraphics[scale=0.25]{./results/plots/ratio_to_optimal_selected_hf.pdf}
		%%		\caption{Comparison of different heuristics for HF.}
		%%		\label{fig:ratio_to_optimal_hf}
		%%	\end{figure*}
		\begin{figure*}[htb]
			\includegraphics[scale=0.5]{./all-binpack/ratio_to_optimal_selected_hf.pdf}
			\caption{Comparison of different heuristics for HF.\todo[inline]{LED: Wouldn't it be easier to read if facet labels were expressed as ratios of $m_c$ ($1$, $1.125$, $1.25$, ...) instead of absolute values? Skumar: It'll provide a nice view but $m_c$ values of both experiments are quite different. In that case, we have to explicitly mention $m_c$ values.}}
			\label{fig:ratio_to_optimal_hf}
		\end{figure*}

@@

		\begin{figure}[htb]
%%			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_hf-best.pdf}
			\includegraphics[scale=0.5]{./results/plots/ratio_to_optimal_hf-best.pdf}
			\caption{Comparision of best variants of all categories for HF.}
%%			\todo[inline]{LED: I still believe you should plot the actual ratio $r$ and not $1/r$. Since I am not sure how to redo the plots I will let you do it. Also ylab(``Ratio to optimal'') please (or more explicitley, to OSIM?). And make sure to write ``Best static'' and remove underscores. You can use plyr::revalue for that.} 
			\label{fig:ratio_to_optimal_best_hf}
		\end{figure}

@@

		\begin{figure}[htb]
%%			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_ccsd-best.pdf}
			\includegraphics[scale=0.5]{./results/plots/ratio_to_optimal_ccsd-best.pdf}
			\caption{Comparision of best variants of all categories for CCSD.}
			\label{fig:ratio_to_optimal_best_ccsd}
		\end{figure}

@@

		\begin{figure*}[htb]
%%			\includegraphics[scale=0.5]{./results/plots/inverse_ratio_to_optimal_batch-best.pdf}
			\includegraphics[scale=0.5]{./results/plots/ratio_to_optimal_batch-best.pdf}
			\caption{Best variants of all categories where heuristics are applied in the batches of 100 tasks.}
%%			\todo[inline]{LED: Here also I believe you should plot the actual ratio $r$ and not $1/r$.}
			\label{fig:best_variants_batch}
		\end{figure*}
